Network Cascades

### 2016-08-22 paper/paper.tex
Explain the weird integral property

Then each agent is given a threshold $\phi \in [0,1]$, drawn from an arbitrary random distribution TODO with some weird integral property. Relating to the example, this represents the ``convincability'' of a person.

>>>>

Then each agent is given a threshold $\phi \in [0,1]$, drawn from an arbitrary random distribution $f(\phi): [0,1] \rightarrow [0,1]$ which must be normalized such that $\int_0^1 f(\phi) d\phi = 1$, i.e. the area beneath the propability function is 1, which means that all distributions must allocate the same total of propabilities, which makes them comparable among each other. Relating to the example, this represents the ``convincability'' of a person.
